\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{xcolor}
\usepackage{anyfontsize}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/xiao-hu-6bab19191/}{\Large Xiao Hu}} & \href{mailto:xhu23@buffalo.edu}{xhu23@buffalo.edu}\\
  & 513-291-5538\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The State University of New York at Buffalo}{Buffalo, NY}
      {Master of Science in Data Science}{Jan. 2022 -- May. 2023}
    \resumeItemListStart
        \resumeItem{Select Coursework}
          {Data Science, Machine Learning, Cybersecurity}
    \resumeItemListEnd
    \resumeSubheading
      {Miami University}{Oxford, OH}
      {Bachelor’s Degree in Computer and Information Science}{Aug. 2016 -- Dec. 2021}
    \resumeItemListStart
        \resumeItem{Select Coursework}
          {Algorithms, Cloud Computing, Database Systems, Networking}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tencent Music}{}
      {Group Member of Hypermedia Department}{July. 2021 - Aug. 2021}
      \resumeItemListStart
        \resumeItem{User Preference Analysis}
          {Analyzed playlists to compute user preferences and action trajectories, providing support for page design and optimization.}
        \resumeItem{Implementing Requirements}
          {Implemented page functional planning and development, wrote high-quality code, and ensured compliance with regulatory requirements}
        \resumeItem{Front-end Development}
          {Developed, debugged, and maintained product functionality using HTML and JavaScript to optimize application performance.}
        \resumeItem{Database Optimization}
          {Supported real-time data processing, fault analysis, and performance optimization of SQL databases.}
        \resumeItem{Testing}
          {Performed functional testing and emergency bug fixes before the go-live.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Web Application: "WhenToMeet"}{}
      {Capstone \& Design Class}{Sep. 2021 - Dec. 2021}
      \resumeItemListStart
        \resumeItem{Project Background}
          {Allows instructors to determine the optimal meeting time for each group and auto-assign students to projects.}
        \resumeItem{Back-end Development}
          {Implemented core algorithms using Java; utilized MySQL for the database.}
        \resumeItem{UX/UI Design}
          {Improved user experience/interface design according to feedback from users.}
        \resumeItem{Result}
          {Developed a web-app that resolved the scheduling problem while also addressing privacy factors that prevent instructors from seeing student schedules and protected the information of each user.}
    \resumeItemListEnd

    \resumeSubheading
      {Global Population Research Project}{}
      {Database Management Systems}{Sep. 2022 - Dec. 2022}
      \resumeItemListStart
        \resumeItem{Project Background}
          {Complete discussions and research on global population issues.}
        \resumeItem{SQL Optimization}
          {Optimized the database to improve query efficiency and sanitize data.}
        \resumeItem{Automation}
          {Used Python, SQL and a Google Sandbox Library dataset to deploy data automation scripts.}
        \resumeItem{Result}
          {Research has shown that population size is related to average life expectancy and not to fertility rate.}          
      \resumeItemListEnd

    \resumeSubheading
      {Buffalo City Transportation Research Project}{}
      {Programming and Database Fundamentals}{Jan. 2022 - May. 2022}
      \resumeItemListStart
        \resumeItem{Project Background}
          {Analyzes datasets that can predict safe areas for students to live in.}
        \resumeItem{Data Sanitation}
          {Cleaned and scaled the dataset from the traffic database of Buffalo; removed outliers to help the data conform to the model.}
        \resumeItem{Model Evaluation}
          {Utilized R and Python to implement the regression and prediction sections and compared the results to evaluate the best model.}
        \resumeItem{Result}
          {Improved model accuracy such that it could infer which area is safer.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  



%-----------SKILLS & CERTS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Technical}
      {Python, Java, R, HTML, CSS, JavaScript, C++, PHP, MySQL}
    \resumeSubItem{Professional}
      {Software Development, Front-end \& Back-end Web Development, Machine Learning}
    \resumeSubItem{Language}
      {English (Fluent), Mandarin (Native)}
  \resumeSubHeadingListEnd
%
\end{document}


